Adaptive Scheduling of Scientific Workflows

### 2024-03-11 main.tex
description of baseline (HEFT with memories)

    \subsection{Various useful approaches}

    Bader et al. developed a system that identifies task similarities.
    Given a workflow, it returns tasks similar to a given task.
    We can use this system in our modelling and say that we know the new weights for finished tasks and will modify future tasks in accordance to their similarity.
    For example, if a task finished 2 times later than expected, then all future similar tasks will be assumed to finish 2 times later.

    \subsection{Local search}
    One strategy that can be used is local search, a similar approach as with swaps.
    The starting point could be a previously valid solution (for example, one by HetPart).
    In the first step, the solution would need to become valid again.
    Then, we repartition blocks on the critical path  and merge blocks in attempt to improve makespan.
    Finally, we swap blocks between processors to finish makespan improvement.

>>>>

    \subsection{Baseline: HEFT with memories}

    \algo{HEFT} is one of the most popular scheduling heuristics(TODO cite).
    This algorithm schedules tasks on heterogeneous computing systems with the aim to minimize
    the workflow's overall completion time.
    The classical formulation of \algo{HEFT} does not respect memory boundaries, so we suggest a
    slightly changed version that also takes memory sizes into account.

    \algo{HEFT} first assigns all tasks their ranks on all processors.
    This rank includes the bottom level of the task, including the maximum cost of its successors on the same processor.
    Then, for each task, they are being assigned to the processor with the best rank.
    Finally, the algorithm calculates the order of execution of tasks on each processor, depending on their dependencies.

    We only change the assignment to processor part.
    Before assigning a new task there, we calculate the memory requirement of already assigned tasks.
    If the remaining memory is big enough to host the task, we assign it there, otherwise we try the next-best processor
    rank-wise.

    \skug{Even easier: calculate the memory requirement of already assigned tasks by summing them up. This will lead
    to an overestimation of memory requirement.}

    \subsection{New heuristic: Local search}
    One strategy that can be used is local search, a similar approach as with swaps.
    The starting point could be a previously valid solution (for example, one by HetPart).
    In the first step, the solution would need to become valid again.
    Then, we repartition blocks on the critical path  and merge blocks in attempt to improve makespan.
    Finally, we swap blocks between processors to finish makespan improvement.
